Peer Assessments in Practical Machine Learning
========================================================

I apologize for this totally unfinished report. I was not able to start work on this up until 3 hours before deadline. My algorithm works as follows: 

1. Use only quantitative variables that have non-missing values and "user" variable
2. For each user separately, scale the data, and use nearest neighbor to optimize the number of neighbor (based on CV)
3. Appply this to the testing data.


You can see below my exploratory analysis, but the algorithm testing is not quite finish. I will need to submit the prediction results after the soft deadline.

Sorry.


```{r Read, cache=T}
pml.df  <- read.csv("pml-training.csv", stringsAsFactors = FALSE)
```

You can also embed plots, for example:

#  ```{r fig.width=7, fig.height=6}

```{r Explore, cache=TRUE}
dim(pml.df)
pml.df[1,]
str(pml.df)
```


```{r Explore2, cache=TRUE}
attach(pml.df)
hist(X)
table(user_name)
```

```{r Explore3, cache=TRUE}
CountNA <- function(x) sum(is.na(x))
apply(pml.df,2,CountNA)
```


```{r ReadTest, cache=TRUE}
pml.test.df  <- read.csv("pml-testing.csv", stringsAsFactors = FALSE)
Count.v <- apply(pml.test.df,2,CountNA)
dim(pml.test.df)
Cond <- ((Count.v>0)|(c(T,F,rep(T,5),rep(F,153))))
pml.df2 <- pml.df[,!Cond]
str(pml.df2)
apply(pml.df2,2,CountNA)
```

```{r library}
require(class)
set.seed(10)
```


```{r Prediction, cache=TRUE}
k  <-  ncol(pml.df2)
k
Predict.f <- function(Test.p=0.1,neib.k=10,User="Name") {
   Cond.User <- (pml.df2[,1]==User)
   mat <- pml.df2[Cond.User,]
   Y  <-  as.factor(mat[,k])
   X.mat <- mat[,-c(1,k)]
   X.mat <- scale(X.mat) # should really scale training and then testing the same way, but have not time now 
   n <- nrow(mat)
   Ind <- sample(1:n,floor(n*Test.p))
   train <- X.mat[-Ind,]
   cl <- Y[-Ind]
   test <- X.mat[Ind,]
   Y.pred <- knn(train, test, cl, k = neib.k, l = 0, prob = FALSE, use.all = TRUE)
   Pred.rate <- sum(Y.pred==Y[Ind])/length(Ind)
   Pred.rate
   
}
Predict.f(Test.p=0.1,neib.k=10,User="carlitos")
```


```{r Optimize, cache=TRUE}
pml.test.df2 <- pml.test.df[,!Cond]
str(pml.test.df2)
apply(pml.test.df2,2,CountNA)
dim(pml.test.df2)
Users.v <- unique(pml.test.df2[,1])
Users.v

```

```{r Optimize2, cache=TRUE}
Test.p.val <- 0.1
neib.k.val <- c(1:10)
d <- length(neib.k.val)
m <- length(Users.v)
m
Pred.rate.mat <- matrix(0,d,m)
for (h in 1:m){
   print(h)
   for (j in 1:d) {
      print(h)
      # browser()
      Pred.rate.mat[j,h] <- Predict.f(Test.p=Test.p.val, neib.k=neib.k.val[j], User=Users.v[h])
   }
}
Pred.rate.mat
matplot(neib.k.val,Pred.rate.mat,type="l")

```
   

Please, cite this paper to refer the WLE dataset

Velloso, E.; Bulling, A.; Gellersen, H.; Ugulino, W.; Fuks, H. Qualitative Activity Recognition of Weight Lifting Exercises. Proceedings of 4th International Conference in Cooperation with SIGCHI (Augmented Human '13) . Stuttgart, Germany: ACM SIGCHI, 2013.




